\documentclass[12pt,useAMS]{ociamthesis}  % default square logo 
%\documentclass[12pt,ibeltcrest]{ociamthesis} % use old belt crest logo
%\documentclass[12pt,shieldcrest]{ociamthesis} % use older shield crest logo

%load any additional packages
\usepackage{amssymb}
\usepackage{footnote, enumerate, url, amsmath, color}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{amssymb}

\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\definecolor{titlecol}{rgb}{0,0,0}
\definecolor{titlecol2}{rgb}{0,0.65,0}
\definecolor{titlecol3}{rgb}{0.99,0.4,0.}
\definecolor{minorcol}{rgb}{1,0,0}
%\definecolor{titledark}{rgb}{0,0,0.8}
%\definecolor{hilit}{rgb}{0,0,1}
%\definecolor{hilitdark}{rgb}{0,0,0.8}
%\font\sbf=cmssbx10 at 32.28pt %big font for headers

\font\nbf=cmssbx10 at 12.28pt %big font for headers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% If you want to leave notes in the text feel free to define
%%%% your own colour above and a style below
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\note		{\color{titlecol2} \nbf}
\def\noteb		{\color{titlecol} \nbf}
\def\notebsm	{\color{titlecol}}
\def\notecjl	{\color{titlecol2} \nbf}
\def\notecsm	{\color{titlecol2}}
\def\noterjs	{\color{titlecol3} }
\def\minor		{\color{minorcol}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For the eventual referee response
\def\changed    {\color{titlecol} }
%\def\changed    {}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Other stuff I use a lot
\def\oiii		{$\mathrm{\left[ O \textsc{iii}\right] }$}
\def\moiii		{\mathrm{\left[ O \textsc{iii}\right] }}
\def\nii		{$\mathrm{\left[ N \textsc{ii}\right] }$}
\def\mnii		{\mathrm{\left[ N \textsc{ii}\right] }}
\def\sii		{$\mathrm{\left[ S \textsc{ii}\right] }$}
\def\msii		{\mathrm{\left[ S \textsc{ii}\right] }}
\def\galfit     {{\tt GALFIT}}
\def\gandalf     {{\tt GANDALF}}
\def\emcee      {{\tt emcee}}

\def\msun	       {$\rm{M}_{\odot}$}
\def\mmsun	{\rm{M}_{\odot}}
\def\fnobulge    {$f_{\rm no~bulge}$}
\def\mfnobulge {f_{\rm no~bulge}}
\def\fedgeon     {$f_{\rm edge-on}$}
\def\mfedgeon  {f_{\rm edge-on}}
\def\fcnobulge    {$f_{\rm confirmed~no~bulge}$}
\def\mfcnobulge {f_{\rm confirmed~no~bulge}}
\def\ha               {H$\alpha$}
\def\mha            {{\rm H}\alpha}
\def\mbh           {$M_{\rm BH}$}
\def\mmbh        {M_{\rm BH}}

\def\kappamean {$\overline{\kappa}$}
\def\mkappamean {\overline{\kappa}}

\def\lesssim{\mathrel{\hbox{\rlap{\hbox{\lower3pt\hbox{$\sim$}}}\hbox{\raise2pt\hbox{$<$}}}}}
\def\gtrsim{\mathrel{\hbox{\rlap{\hbox{\lower3pt\hbox{$\sim$}}}\hbox{\raise2pt\hbox{$>$}}}}}


\newcommand\nodata{ ~$\cdots$~ }

%define all that you need to define
\def\starpy {\textsc{starpy}}

%input macros (i.e. write your own macros file called mymacros.tex 
%and uncomment the next line)
%\include{mymacros}

\title{The influence of morphology, AGN and environment on the quenching histories of galaxies}   %note \\[1ex] is a line break in the title

\author{Rebecca Jane Smethurst}             %your name
\college{Pembroke College}  %your college

%\renewcommand{\submittedtext}{change the default text here if needed}
\degree{Doctor of Philosophy}     %the degree
\degreedate{Michaelmas 2016}         %the degree date

%end the preamble and start the document
\begin{document}

%this baselineskip gives sufficient line spacing for an examiner to easily
%markup the thesis with comments
 
%set the number of sectioning levels that get number and appear in the contents
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}


\maketitle                  % create a title page from the preamble info

%\begin{dedication}
%This thesis is dedicated to\\
%all of those\\
%that dare to dream.
%\emph{``The Universe is under no obligation to make sense to you.''} \\- Neil deGrasse Tyson
\newpage
\vspace*{3cm}
\begin{center}
\emph{``All we have to decide, \\ is what to do with the time \\ that is given to us.''} \\\end{center} \begin{flushright}- J.~R.~R. Tolkein\end{flushright}

%\end{dedication}
\newpage

\begin{abstract}  

% What's your big Q?
What drives the transition of galaxies from the disc dominated, star forming blue cloud to the elliptical dominated, quiescent red sequence? What role does the morphology, central supermassive black hole and galaxy environment play in this transition? 
% How do you answer them? STARPY?
I have attempted to answer these questions by using Bayesian statistics to infer a simple star formation history (SFH) describing the time, $t_q$, and exponential rate, $\tau$, that quenching occurs in a galaxy. I use both the optical and NUV photometry of a galaxy in order to infer the posterior distribution of its SFH across the two dimensional $[t_q, \tau]$ parameter space. I then utilise the Galaxy Zoo 2 morphological classifications to obtain a morphology weighted, combined population distribution across each quenching parameter for a sample of galaxies. 
% What do you find in morph chapter?

I apply this method across the blue cloud, green valley and red sequence of a sample of $126,316$ galaxies and find a clear difference between the quenching timescales preferred by smooth and disc weighted populations, with three major routes through the green valley dominated by smooth (rapid rates, attributed to major mergers), intermediately classified (intermediate rates, attributed to galaxy interactions) and disc morphologies (slow rates, attributed to secular evolution). I hypothesise that morphological changes occur in systems which have undergone quenching with an exponential rate, $\tau < 1.5~\rm{Gyr}$, in order for the evolution of galaxies in the green valley to match the ratio of smooth to disc galaxies observed in the red sequence.
% What do you find in AGN feedback chap?

I repeat this SFH analysis for a sample of $1,244$ Type 2 AGN host galaxies and find statistical evidence for recent, rapid quenching, suggesting that this may be caused by AGN feedback. However I find that rapid quenching rates cannot account for all the quenching across the AGN host population; slow quenching rates, attributed to secular evolution, are also significant in the evolution of AGN host galaxies.
% What do you find in bulgeless AGN?

I investigate this possible secular co-evolution of galaxies and black holes further by measuring the black hole masses of a sample of $101$ bulgeless AGN host galaxies and compare them to typical black hole-galaxy scaling relations. I find that the measured black holes of the bulgeless galaxies are $\sim1-2~\rm{dex}$ more massive than they should be, given their lack of bulges. This suggests that black hole-galaxy scaling relations may arise due to mutual correlations to the overall gravitational potential of the dark matter halo of the galaxy. 
% What do you find in environment chapter?

I also considered the effect of the group environment on the time and rate that quenching occurs, with respect to the group-centric radius, for $4,629$ satellite galaxies. I find that although mergers, mass quenching and morphological quenching are all occurring in groups, environmentally driven quenching mechanisms are also prevalent. However, I find that these environmentally driven quenching processes are not correlated with the velocity of a satellite within a group, ruling out ram pressure stripping as a possible mechanism. 
% Sum up your big picture

I discuss how all of these quenching mechanisms are likely to affect a galaxy across its lifetime, acting in concert to reduce the SFR, which in turn produces the wide distribution of quenching timescales seen across the colour-magnitude diagram. I discuss ideas for future work using the method employed in this work, including applying it to forthcoming data from large integral field unit surveys. 

\end{abstract}

\begin{originalitylong}
I carried out the work presented in thesis at the Department of Astrophysics, University of Oxford between October 2013 and December 2016, under the supervision of Prof. Chris Lintott. It was funded by a Science Technology Facilities Council Studentship Grant Code ST/K502236/1. I hereby declare that no part of this thesis has been submitted in support of another degree, diploma or other qualification at the University of Oxford or other higher learning institute. Except where otherwise stated or where reference is made to the work of others, the work in this thesis is entirely my own.

The work in Sections~\ref{chap:starpy}, \ref{chap:morph} \& \ref{sec:agnfeedback} is based on the peer-reviewed, published papers \citealt{smethurst15}, \mnras, 450, 435, and \citealt{smethurst16}, \mnras, 463, 2986, for which I am the lead author {\minor and contributed $\sim85\%$ of the work}. 

The work presented in Section~\ref{sec:intbulgeless} was carried out in collaboration with Dr. Brooke Simmons and Prof. Chris Lintott and is in preparation for submission to \mnras.

The work throughout this thesis relies on observations from the Sloan Digital Sky Survey (SDSS). Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, and the U.S. Department of Energy Office of Science. The SDSS-III web site is \url{http://www.sdss3.org/}.

%SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New York University, Ohio State University, Pennsylvania State University, University of Portsmouth, Princeton University, the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, University of Washington, and Yale University.

The work throughout this thesis is based on observations made with the NASA \emph{Galaxy Evolution Explorer}. GALEX is operated for NASA by the California Institute of Technology under NASA contract NAS5-98034.

This thesis has been made possible by the participation of more than $250,000$ users in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors. galaxyzoo.org}.

This thesis made extensive use of the Tool for Operations on Catalogues And Tables \citep[TOPCAT;][]{taylor05} and the {\tt astropy} Python module \citep{astropy13}. This research has also made use of NASA's ADS service and Cornell's ArXiv.

The copyright of this thesis rests with the author. No quotation from it or information derived from it may be published without the prior consent and acknowledgement of its author. 

\begin{flushright}
Rebecca J. Smethurst
\\
(\emph{December 2016})
\end{flushright}


\end{originalitylong}

\begin{acknowledgements}


I can't quite believe that I've actually written my thesis. It still feels like something I'll have to do eventually; something that needs crossing off the master to-do list. That's not for the lack of hard work that it took to get to this point (trust me!), but more because the last three years and eight weeks have been so enjoyable. Although I had a lot to do with the whole hard work part, I can't claim credit for how much I've enjoyed my DPhil - that all goes to the people in my life that made it so. 

First and foremost I have to thank my supervisor Prof. Chris Lintott. Chris, thank you for taking a chance on me and for bringing me back into the world of astronomy that I had so sorely missed. Somehow, you just understood me from the start; that I mostly wanted to be left to my own devices and that buying me the occasional rum wouldn't go amiss. I suppose I should also mention all those hours we met to talk science - that was pretty useful too, I guess. In all seriousness though, I'm honoured to have been your first graduate student and I can't imagine having been supervised by anybody else. 

A massive thank you also has to go to Dr. Brooke Simmons. Brooke, I lost count a long time ago of how many times you made me laugh so hard it hurt. Thank you for making observing, working on a paper and going to conferences some of the most fun experiences of my life. With those two trips to visit you in San Diego I've just about forgiven you for leaving! You are literally the best friend and colleague anyone could wish for and always have the best advice for those following in your footsteps. And the best Taylor Swift GIFs, obviously. 

Thanks also have to go to the entire Galaxy Zoo Team for their support and collaboration over the past three years. In particular Dr. Karen Masters for her advice and genuine interest in my career; thank you Karen for showing me that the dream is real.

Three years of PhD life would be truly impossible without a group of friends you can count on to make you laugh, cry and get the drinks in. I am lucky enough to have many of those. To my office mates over the past three years, thank you for putting up with my oddities and for making me laugh with yours. To my fellow PhD students, thank you for sharing this experience with me and being there with some cake or a chat whenever needed. To all those at Pembroke, thank you for providing me with a home away from home and being my \emph{Cheers} bar. To anyone who has ever been part of the Zooniverse family: I've never known a more wonderful, eclectic group of people and I'll be forever grateful to have been welcomed in for all the hijinks. To all my friends from home and from Durham, thank you for reminding me that there is a world outside of academia and for helping me pop the Oxford bubble once in a while.

Special mention has to go to Laura, Ricarda, Ali, Grant, Mark, Sarah, Christina, Will, and Malte. For all of the pub trips, poker nights, formals, bops and bar nights. Only time will tell what effect you wonderful people have had on my liver.

Thanks must also go to the genius that is Gilmore Girls for bringing me much needed joy every evening when I got home after a long day writing. Seven seasons and seven thesis sections - coincidence? I think not! Music has been an exceptional source of motivation during my write up; with the entire thing written under the influence of a list of artists which would probably be longer than my thesis. As I write these acknowledgements, I'm listening to The Boss, which feels appropriate. 

I'm not sure if the fact that I'm listening to Bruce Springsteen as I type this or the fact that I've actually completed my thesis will make my parents more proud; it's a pretty close call! Mum \& Dad, I don't think there's enough trees on this planet to make enough paper for me to write down how grateful I am for everything you've ever done for me. You always told me there was nothing I couldn't do if I set my mind to it, you gave me every opportunity and you trusted me to make the right decisions about my life. I hope what I've decided to do with it makes you proud, because I am one proud daughter. I'm also one proud sister. Meg, during the past three years I've got to watch you grow from my crazy, wonderful little sister into the crazy, smart young woman who walks around Bath like she's always lived there. Thank you for being my best friend, for sharing in my crazy and for bringing so much laughter into my life. You're my person.

So I'm already weeping at my desk but there's still one person left to thank. Sam, you are the best thing in my life. I count myself lucky for every day I get to spend with you. Thank you for supporting me every step of the way through my PhD, even if it meant spending time apart. Thank you for being the other half of my crazy and for bringing so much joy to my days. I still maintain that the only person who will ever read my thesis as thoroughly as I did, is you. I'd say I can't believe you did that for me, but I can. 

Oy with the poodles already!


\begin{flushright}
Becky 
\\
(\emph{December 2016})
\end{flushright}

\end{acknowledgements}

\begin{romanpages}          % start roman page numbering
\tableofcontents            % generate and include a table of contents
\listoffigures              % generate and include a list of figures
\end{romanpages}            % end roman page numbering


\baselineskip=18pt plus1pt
\linespread{1.2}
 \setlength{\parskip}{1em}
 
%now include the files of latex for each of the chapters etc
\include{introduction/introduction}
\include{starpy/starpy}
\include{morphology/morph}
\include{agn/agn}
\include{environment/environment}
\include{discussion/discussion}
%\include{conclusion/conclusions}


%next line adds the Bibliography to the contents page
\addcontentsline{toc}{chapter}{Bibliography}
%uncomment next line to change bibliography name to references
%\renewcommand{\bibname}{References}
\bibliographystyle{mn2e}
\bibliography{refs}        %use a bibtex bibliography file refs.bib

\newpage
\vspace*{3cm}

\begin{center}

\emph{Mischief Managed.}
\end{center}


\end{document}


